Palaeobiology demo: disparity-through-time and within groups

### 2022-02-15 inst/gitbook/03_specific-tutorials.Rmd
Minor updates on the gitbook

```{r, warning = FALSE}
## Create a custom subsets object
dummy_groups <- custom.subsets(dummy_space,
                               group = list("group1" = 1:5,
                                            "group2" = 6:10))
summary(dispRity(dummy_groups, metric = centroids,
    centroid = colMeans(matrix.dispRity(dummy_groups, "group1"))))
```

@@

```{r, fig.height = 16, fig.width = 6}
## The results as a dispRity object
example_test

@@

 * `quantiles` values for the confidence interval levels (by default, the 50 and 95 quantiles are calculated)
 * `cent.tend` for the central tendency to use for summarising the results (default is `median`)
 * digits` option corresponding to the number of decimal places to print (default is `2`)
 * `recall` option for printing the call of the `dispRity` object as well (default is `FALSE`)

@@

>>>>

```{r, warning = FALSE}
## Create a custom subsets object
dummy_groups <- custom.subsets(dummy_space,
                               group = list("group1" = 1:5,
                                            "group2" = 6:10))
summary(dispRity(dummy_groups, metric = centroids,
    centroid = colMeans(get.matrix(dummy_groups, "group1"))))
```

@@

```{r, fig.height = 12, fig.width = 6}
## The results as a dispRity object
example_test

@@

 * `quantiles` values for the confidence interval levels (by default, the 50 and 95 quantiles are calculated)
 * `cent.tend` for the central tendency to use for summarising the results (default is `median`)
 * `digits` option corresponding to the number of decimal places to print (default is `2`)
 * `recall` option for printing the call of the `dispRity` object as well (default is `FALSE`)

@@

### Graphical options

### 2022-02-15 inst/gitbook/08_palaeo-demo.Rmd
Minor updates on the gitbook

```{r, fig.height = 16, fig.width = 8}
my_test <- test.metric(my_matrix, metric = c(sum, variances), shifts = c("random", "size"))
summary(my_test)
plot(my_test)
```

@@

```{r}
## Calculating disparity for the bootstrapped and rarefied data
disparity <- dispRity(rare_bin_morphospace , metric = c(sum, variances))
```

>>>>

```{r, fig.height = 16, fig.width = 8}
my_test <- test.metric(my_matrix, metric = c(sum, dispRity::variances), shifts = c("random", "size"))
summary(my_test)
plot(my_test)
```

@@

```{r}
## Calculating disparity for the bootstrapped and rarefied data
disparity <- dispRity(rare_bin_morphospace , metric = c(sum, dispRity::variances))
```
